\documentclass[11pt, a4paper]{article} 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}  
\usepackage[left = 0mm, right = 0mm, top = 0mm, bottom = 0mm]{geometry}
\usepackage[stretch = 25, shrink = 25, tracking=true, letterspace=30]{microtype}  
\usepackage{xcolor}
\usepackage{fontawesome5}

\usepackage{enumitem}        % To redefine spacing in lists
\setlist{parsep = 0pt, topsep = 0pt, partopsep = 1pt, itemsep = 1pt, leftmargin = 6mm}

\usepackage{FiraSans}        % Change this to use any font, but keep it simple
\renewcommand{\familydefault}{\sfdefault}

\definecolor{cvblue1}{HTML}{1d3557}
\definecolor{cvblue2}{HTML}{457b9d}

%%%%%%% USER COMMAND DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%
% These are the real workhorses of this template
\newcommand{\dates}[1]{\hfill\mbox{\textbf{#1}}} % Bold stuff that doesn’t got broken into lines
\newcommand{\is}{\par\vskip.5ex plus .4ex} % Item spacing
\newcommand{\smaller}[1]{{\small$\diamond$\ #1}}
\newcommand{\headleft}[1]{\vspace*{3ex}\textsc{\textbf{#1}}\par%
    \vspace*{-1.5ex}\hrulefill\par\vspace*{0.7ex}}
\newcommand{\headright}[1]{\vspace*{2.5ex}\textsc{\Large\color{cvblue}#1}\par%
     \vspace*{-2ex}{\color{cvblue}\hrulefill}\par}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[colorlinks = true, urlcolor = white, linkcolor = white]{hyperref}

\begin{document}

% Style definitions -- killing the unnecessary space and adding the skips explicitly
\setlength{\topskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\fboxsep}{0pt}
\pagestyle{empty}
\raggedbottom

\begin{minipage}[t]{0.33\textwidth} %% Left column -- outer definition
%  Left column -- top dark rectangle
\colorbox{cvblue1!80}{\begin{minipage}[t][5mm][t]{\textwidth}\null\hfill\null\end{minipage}}

\vspace{-.2ex} % Eliminates the small gap
\colorbox{cvblue2}{\color{white}  %% LEFT BOX
\kern0.09\textwidth\relax% Left margin provided explicitly
\begin{minipage}[t][293mm][t]{0.82\textwidth}
\raggedright
\vspace*{2.5ex}

\Large Jasper \textbf{\textsc{van Turnhout}} \normalsize 

\vspace*{0.5ex} % Extra space after the picture

\headleft{Profile Summary}
Senior Engineer with over 20+ years of expertise in C++, Python, Machine Learning and Computer Vision. Experience in developing cross-platform Computer Vision SDKs, building and managing data pipelines, creating and deploying production-ready software solutions.

\headleft{Contact details}
\small % To fit more content
\faIcon{envelope} \href{mailto:jturnhout@gmail.com}{jturnhout@gmail.com}\\
\faIcon{linkedin} \href{https://linkedin.com/in/jasper-van-turnhout/}{/jasper-van-turnhout}\\
\faIcon{github} \href{https://github.com/Jabba}{/Jabba}
\normalsize

\headleft{Personal information}
\small Citizenship: \textbf{Dutch} \\[0.5ex]
\small Languages: \textbf{English}, \textbf{Dutch} \\[0.5ex]
\small City: \textbf{Amsterdam}
\normalsize

\headleft{Skills}
\begin{itemize}
\item Programming Languages: C++, C, Python, Java, Android, JNI, JavaScript, PHP
\item Frameworks \& Libraries: OpenCV, POCO, OpenVINO, cURL, TensorFlow, Django, Flask, Panda
\item Databases: MySQL, MongoDB, SQLite
\item Cloud: AWS, Azure
\item Tools: Docker, Ansible, Jenkins, Jira, Github, Bitbucket
\item OS: Ubuntu, Windows, Balena
\end{itemize} 

\end{minipage}%
\kern0.09\textwidth\relax%%Right margin provided explicitly to stretch the colourbox
}
\end{minipage}% Right column
\hskip2.5em% Left margin for the white area
\begin{minipage}[t]{0.56\textwidth}
\setlength{\parskip}{0.8ex}% Adds spaces between paragraphs; use \\ to add new lines without this space. Shrink this amount to fit more data vertically

\vspace{2ex}

\headright{Experience}
\textbf{Senior Engineer} \hfill 2011--2025 \\
\textit{ThirdSight → Sightcorp → Raydiant (acquisitions)} \\
\small
Progressive engineering role across three companies through acquisitions. Specialized in cross-platform Face Analysis technology for Windows, Linux and Android, with native deep learning integration. Contributed to SDK development, product development, CI/CD infrastructure, and system integration within commercial platforms.

\vspace{0.5em}

\textsc{Raydiant} \hfill 2022--2025 \\
\smaller{Integrated Face Analysis into Raydiant’s Experience Platform. Led AI team and built CI/CD pipelines for the Face Analysis SDK and Toolkit. Develop and iterate over advanced detectors and estimators using modern deep learning frameworks and accelerators.}

\textsc{Sightcorp} \hfill 2013--2022 \\
\smaller{Engineered native cross-platform SDKs and toolkits for Face Analysis across Windows, Linux, and Android. Applied deep learning and hardware acceleration techniques to optimize performance and accuracy.}

\textsc{ThirdSight} -- Scientific Programmer \hfill 2011--2013 \\
\smaller{Developed early-stage cross-platform Face Analysis SDKs. Trained and evaluated models for demographics, facial expressions, and head pose estimation using statistical and classic machine learning and computer vision methods.}

\textbf{Interface Designer} \dates{2010--2011} \\
\textit{Q-Go → RightNow → Oracle (acquisitions)} \\
Role continued across 3 companies through acquisitions. Core focus: UX/UI design and prototyping for customers of the Q-Go/Rightnow Customer Service.

\textsc{RightNow (formerly Q-Go)} \hfill 2011 \\
\smaller{Transitioned design and customer tools post-acquisition. Expanded mockups and design standards for new clients in new international markets.}

\textsc{Q-Go} \hfill 2010 \\
\smaller{Created customer-facing UI mockups and supported sales with frontend prototyping.}
\is

\textbf{Webmaster} at \textit{ING Lease.}  \dates{2007-2008} \\
\smaller{Maintaining the Internet sites of ING Lease Europe and the intranet of ING Lease Netherlands.}
\is

\headright{Education}

\textsc{Master of Science in Artificial Intelligence} \textit{University of Amsterdam}. \dates{2008--2010} \\

\is
\textsc{Bachelor of Science in Artifical Intelligence} \textit{University of Amsterdam}.  \dates{2003--2007} \\

\headright{Hobbies}

\textit{Synthesizes \& Ableton, Video game development for retro systems (Atari-based), Snowboarding, Hiking}
\end{minipage}

\end{document}
